### 2015-01-16 publish/plos_template.tex
updated rendering figure and scaled figures, added caption to photos

\section*{Figure Legends}
% This section is for figure legends only, do not include
% graphics in your manuscript file.
%
%\begin{figure}
%\includegraphics[scale=1]{file.png} % take image out for final manuscript
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}

\begin{figure}
\includegraphics[scale=1]{figure-images/rendering-assembly4.jpg} % take image out for final manuscript
\caption{
{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adaptor for pipette tips.
}
\label{CAD-render-figure}
\end{figure}

\begin{figure}
\includegraphics[scale=1]{figure-images/pipette-disassembled.JPG} % take image out for final manuscript
\includegraphics[scale=1]{figure-images/pipette-assembled.JPG} % take image out for final manuscript
\caption{
{\bf Bold the first sentence.}  Rest of figure caption.  
}
\label{photo-parts-figure}
\end{figure}

>>>>

\section*{Figure Legends}
% This section is for figure legends only, do not include3
% graphics in your manuscript file.
%
%\begin{figure}
%\includegraphics[scale=1]{file.png} % take image out for final manuscript
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}

\begin{figure}
\includegraphics[scale=0.4]{figure-images/rendering-assembly4.png} % take image out for final manuscript
\caption{
{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adaptor for pipette tips.
}
\label{CAD-render-figure}
\end{figure}

\begin{figure}
\includegraphics[scale=0.04]{figure-images/pipette-disassembled.JPG} % take image out for final manuscript
\includegraphics[scale=0.04]{figure-images/pipette-assembled.JPG} % take image out for final manuscript
\caption{
{\bf Photos of pipette.}  The pipette is composed of three printed parts, a 1 mL syringe and some additional hardware.  
}
\label{photo-parts-figure}
\end{figure}
